\documentclass{cv}

\begin{document}

% Name, phone, email, address
\begin{cvHeader} 
\printName{Chi-I Huang (Jason)}
\printPhone{+886 933 020145}
\printEmail{jasson15@gmail.com}
\printWebsite{http://jasson15.github.io}
\printAddress{No.92, Futai St., Situn Dist., Taichung City 407, Taiwan}
\end{cvHeader}

%------------------------------------------------------------------------------
% Education
%------------------------------------------------------------------------------

\begin{cvSection}{Education}

\begin{experienceSubsection}
{National Taiwan University}
{Taipei, Taiwan}
{\DTMDate{2009-09-01} - \DTMDate{2013-06-01}}
{B.S. in Computer Science and Information Engineering}
\item Overall GPA: 3.79/4.0, Major GPA: 3.93/4.0
\item Coursework: Machine Learning, Multimedia Analysis and Indexing, Data Structures and Algorithms, Cryptography, Compiler Design, Formal Languages and Automata Theory
\end{experienceSubsection}

\begin{eduSubsection}{Continuing Education}{Online Certifications}{\DTMDate{2015-01-01} - \DTMDate{2015-07-01}}
\item *Mining Massive Datasets, Stanford University \href{https://drive.google.com/uc?export=download&id=0B8Evfo4JjbBSTDFIa212ckQ4UUU}{[pdf]} % 98.7\% with Distinction
\item Introduction to Big Data with Apache Spark, the University of California, Berkeley \href{https://s3.amazonaws.com/verify.edx.org/downloads/8e52b92f46154cddbecd6b089df1083e/Certificate.pdf}{[pdf]} % final grade: 100\%, June - July 2015
\item Design and Development of Games for Learning, the Massachusetts Institute of Technology \href{https://s3.amazonaws.com/verify.edx.org/downloads/65152ce5fadb4f5d8b16add38babedaf/Certificate.pdf}{[pdf]} % final grade: 92\%, Apr - June 2015
\item Gamification, the University of Pennsylvania \href{https://drive.google.com/uc?export=download&id=0B8Evfo4JjbBSZjFIdl9XMWFnVXM}{[pdf]} % 95.8\%

\hfill {\footnotesize *: Statement of Achievement with Distinction}
% \item Pattern Discovery in Data Mining, University of Illinois at Urbana-Champaign % 88.2\%

\end{eduSubsection}

\end{cvSection}

%------------------------------------------------------------------------------
% Experience
%------------------------------------------------------------------------------

\begin{cvSection}{Work Experience}

\begin{experienceSubsection}{Wavenet Technology Co., Ltd.}{Taipei, Taiwan}{\DTMDate{2015-02-01} - Present}{Software Architect}

\item Led a 4-member team to pioneer edge-cutting Big Data technologies.
\item Developed a multi-threading web service for real-time bidding (RTB) to suffice the requirement that $99\%$ of the bid requests are replied within $100$ms with $1000$ QPS.
\item Designed a bidding strategy to minimize cost per click (CPC) according to click prediction models while spending campaign budget smoothly.
\item Designed an automated update process to regularly train and deploy the prediction models with Spark machine learning library.
\item Designed an automated bidding report generation pipeline with MapReduce to calculate high dimension bidding insights from 10 million data per day.
% \item Optimized NoSQL queries to suffice the requirement that $99\%$ of the bid requests are replied within $100$ms with $1000$ QPS.
% \item Deployed and maintained computation resources on Spark and Hadoop cluster.
% \item Designed conversion contribution calculation kernel.
% \item Designed cookie tracking pixels and entity resolution.
% \item Built testing framework for code quality via Mocha.
% \item Deployed alert manager for node failure detection.

\end{experienceSubsection}

\begin{experienceSubsection}{Air Force}{Taiwan}{\DTMDate{2013-06-01} - \DTMDate{2014-05-01}}{Airman, Mandatory Military Service}

\item Provided a group commander with private administrative and clerical aid.

\end{experienceSubsection}

\begin{experienceSubsection}{InfoKeyVault Co., Ltd.}{Taipei, Taiwan}{\DTMDate{2011-07-01} - \DTMDate{2011-08-01}}{Programmer, Intern}

\item Analyzed endurance of security USB tokens after executing encryptions and decryptions over 1,000,000 times via Visual Studio
\item Cooperated with an e-commerce company on a Java gift card system project

\end{experienceSubsection}

\end{cvSection}

% For aesthetic
% \pagebreak

%------------------------------------------------------------------------------
% Selected Projects
%------------------------------------------------------------------------------

\begin{cvSection}{Selected Projects}

\begin{projectSubsection}{Crazy Fruit Market  \href{http://jasson15.github.io/crazy-fruit-market}{[link]}}{\DTMDate{2015-04-01} - \DTMDate{2015-06-01}}{Advanced Vocabulary Learning Game}

\item Crazy Fruit Market is a piece of coursework of Design and Development of Games for Learning, MIT.
\item Facilitated the learning process of ESL learners of advanced English vocabularies.
\item Built a cross-device game by introducing the Cocos2d game engine.
\item Facilitated deployment process and environment setup by containerizing the project into Docker images.
\item Built up a game development chain from scratch, including art design, educational material design and software engineering.
\item Cocos2d, JavaScript, GIMP, Docker

\end{projectSubsection}

\begin{projectSubsection}
{Face Annotation \href{http://cmlab.csie.ntu.edu.tw/~pi/face_annotation}{[link]}}
{\DTMDate{2012-07-01} - \DTMDate{2013-06-01}}
{Web-based Facial Data Annotation Tool}
\item Provided 4,000+ facial data in Hao-Ting Chang's master's thesis, ``Context-augmented profile face attributes detection''.
\item Developed visual markers to mark face and eye positions by dragging and dropping the markers.
\item Documented the whole architecture and detailed programming guides on the project website, guiding site administrators to install, configure and customize their own facial data annotating websites.
\item HTML5, JavaScript, PHP, MySQL

\end{projectSubsection}

\begin{projectSubsection}
{Eventy}
{\DTMDate{2012-05-01} - \DTMDate{2012-12-01}}
{Social network startup which attracted ~200 users in 2 weeks}
% \item Met angel investors.
\item Activated Chinese indexing in our search engine via the Chinese segment algorithm within Coreseek.
\item Achieved real time index update, which updates index every 5 minutes.

\end{projectSubsection}


\begin{projectSubsection}
{Machine Learning \href{http://main.learner.csie.ntu.edu.tw/php/ml12fall/scoreboardeachteam.php?start400=29&end400=100}{[link]}}
{\DTMDate{2012-11-01} - \DTMDate{2013-01-01}}
{Team Competition on Course}

\item Predicted with AUC $0.74$ from $90,000$ 72-dimensional missing value data.
\item Improved ranking from the $46^{th}$ to the $37^{th}$ by adapting a new method to fill missing data via Amelia.
\item Improved ranking from the $37^{th}$ to the $30^{th}$ by utilizing the k-NN learning algorithm.
\item Analyzed performance of several algorithms, such as LIBLINEAR, LIBSVM and k-NN.

\end{projectSubsection}

\end{cvSection}

%------------------------------------------------------------------------------
% Extracurricular Activities
%------------------------------------------------------------------------------

% \begin{cvSection}{Extracurricular Activities}

% \begin{experienceSubsection}{Taiwan Fund for Children and Families}{Taipei, Taiwan}{\DTMDate{2012-05-01} - \DTMDate{2012-06-01}}{Volunteer English Tutor}

% \item Taught English to a teenager 1.5 hour every week.

% \end{experienceSubsection}

% \end{cvSection}

%------------------------------------------------------------------------------
% Skills
%------------------------------------------------------------------------------

\begin{cvSection}{Skills}

\begin{itemize}[label=$\cdot$,leftmargin=0em]

\item Programming: JavaScript, NoSQL, Spark, C, Java, Python, Docker
\item Languages: English (fluent), Japanese (basic), Chinese (native)
\item Standardized Tests: GRE (V160, Q167, AWA3.5), TOEFL iBT (107), TOEIC (885)

\end{itemize}

\end{cvSection}

\end{document}
